Portfolio prioritization of salmon conservation

### 2013-04-09 inst/examples/salmonport.tex
copy sent to committee before 2013-04-08
updating whole project

% my modifications:
\usepackage{fontspec}
\usepackage{booktabs}
\usepackage{mathptmx}
\defaultfontfeatures{Ligatures=TeX}
\setsansfont{Calibri}
\setmonofont{Inconsolata}
\setmainfont{Linux Libertine}
%\setmainfont{Times New Roman}
%\setmainfont{Calibri}
%\setmainfont{Helvetica}
\DeclareTextCommandDefault{\nobreakspace}{\leavevmode\nobreak\ }
\widowpenalty=1000
\clubpenalty=1000
\usepackage{setspace}
\onehalfspacing
%\doublespacing

@@

@@

\begin{figure}[htbp]
\centering
\includegraphics{figure/unnamed-chunk-1.pdf}
\caption{Example Ricker curves for the minimum-variance metapopulation.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{figure/plot-weights-median.pdf}
\caption{Median (solid line) and 25th and 75th quantiles of the weights
across 40 minimum-variance portfolios. Just another way of looking at
it.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{figure/plot-cons-plans-mv.pdf}
\caption{Conservation plans in mean-variance space. The dots show
portfolios from individual simulation runs. The dark and light shaded
areas show 25\% and 75\% quartiles. The left panel shows a scenario with
a stationary environmental signal and strong short-term environmental
noise. The right panel shows a scenario with a linearly-increasing
environmental signal and minimal short-term environmental noise. These
two scenarios bound the two environmental extremes: strong short-term
noise with minimal long-term signal vs.~a strong long-term signal with
minimal short-term signal. Notice what happens to the two \emph{half}
conservation strategies. A more realistic scenario combines the two. The
efficient frontier is shown for the displayed portfolios. This isn't
necessarily the overall efficient frontier.}
\end{figure}

@@

\section{Take home messages}

>>>>

% my modifications:
\usepackage{fontspec}
\usepackage{booktabs}
\usepackage{mathptmx}
\defaultfontfeatures{Ligatures=TeX}
\setsansfont{Calibri}
\setmonofont{Inconsolata}
\setmainfont{Linux Libertine}
%\setmainfont{Times New Roman}
%\setmainfont{Calibri}
%\setmainfont{Helvetica}
\DeclareTextCommandDefault{\nobreakspace}{\leavevmode\nobreak\ }
\widowpenalty=1000
\clubpenalty=1000
\usepackage{setspace}
\onehalfspacing
%\doublespacing
\usepackage{pdflscape}
\usepackage{pdfpages}

@@

\emph{Other title ideas:}\\- Portfolio optimization reveals\ldots{}\\-
something more general with animals instead of just salmon?\\- Portfolio
theory reveals conservation strategies that\ldots{}\\- Intelligent
tinkering with ecological portfolios: patterns of environmental response
diversity drive salmon conservation priorities\\- Keeping every cog and
wheel\ldots{}

@@

\begin{figure}[htbp]
\centering
\includegraphics{figure/unnamed-chunk-1.pdf}
\caption{Example Ricker curves for the minimum-variance metapopulation.
(Ignore right now)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{figure/plot-weights-median.pdf}
\caption{Median (solid line) and 25th and 75th quantiles of the weights
across 40 minimum-variance portfolios. Just another way of looking at
it. (Nothing to see here right now.)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{figure/plot-cons-plans-mv.pdf}
\caption{Conservation plans in mean-variance space. The dots show
portfolios from individual simulation runs. The dark and light shaded
areas show 25\% and 75\% quartiles. The left panel shows a scenario with
a stationary environmental signal and strong short-term environmental
noise. The right panel shows a scenario with a linearly-increasing
environmental signal and minimal short-term environmental noise. These
two scenarios bound the two environmental extremes: strong short-term
noise with minimal long-term signal vs.~a strong long-term signal with
minimal short-term signal. Notice what happens to the two \emph{half}
conservation strategies. A more realistic scenario combines the two
kinds of environmental noise. The efficient frontier is shown for the
displayed portfolios. This isn't necessarily the overall efficient
frontier.}
\end{figure}

@@

\section{Some thoughts on the results}
